---
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: false
geometry: "margin=0.6in"
fontsize: 10pt
header-includes:
  - \usepackage{booktabs}
  - \usepackage{array}
  - \usepackage{tabu}
  - \usepackage{colortbl}
  - \usepackage{xcolor}
  - \definecolor{passgreen}{HTML}{27AE60}
  - \definecolor{failred}{HTML}{E74C3C}
  - \definecolor{revieworange}{HTML}{F39C12}
  - \definecolor{headergreen}{HTML}{2D5F3F}
  - \definecolor{lightgray}{HTML}{F5F5F5}
  - \pagestyle{empty}
params:
  report_data: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
rd <- params$report_data
```

\begin{center}
{\color{headergreen}\rule{\textwidth}{2pt}}
\vspace{4pt}
{\LARGE\bfseries\color{headergreen} LandScan --- Drone QA/QC Flight Report}
\vspace{2pt}
{\color{headergreen}\rule{\textwidth}{2pt}}
\end{center}

\vspace{-4pt}

\begin{flushright}
\small\textit{Generated: `r rd$report_generated`}
\end{flushright}

\vspace{-8pt}

## Mission Information

```{r mission-info}
mission_info <- data.frame(
  Field = c("Ranch", "Block(s) Flown", "Operator",
            "Flight Date", "Flight Time", "Wind Speed"),
  Value = c(rd$ranch, rd$blocks, rd$operator_name,
            rd$flight_date, rd$flight_time, rd$wind_speed),
  stringsAsFactors = FALSE
)
knitr::kable(mission_info, col.names = NULL, format = "latex",
             booktabs = TRUE, linesep = "") |>
  kableExtra::kable_styling(latex_options = "hold_position", full_width = TRUE) |>
  kableExtra::column_spec(1, bold = TRUE, width = "2.2in")
```

## Flight Summary

```{r flight-summary}
solar_val <- if (!is.null(rd$solar_elevation)) rd$solar_elevation else "N/A"
flight_info <- data.frame(
  Field = c("Duration", "Total Images", "Bands Used", "Camera Rig / Model",
            "AGL", "Avg Ground Speed", "Solar Elevation", "Shutter Count", "Source Folder"),
  Value = c(rd$flight_duration, as.character(rd$total_images), rd$bands_used,
            rd$camera_rig, rd$agl, rd$speed, solar_val, rd$shutter_count, rd$source_files),
  stringsAsFactors = FALSE
)
knitr::kable(flight_info, col.names = NULL, format = "latex",
             booktabs = TRUE, linesep = "") |>
  kableExtra::kable_styling(latex_options = "hold_position", full_width = TRUE) |>
  kableExtra::column_spec(1, bold = TRUE, width = "2.2in")
```

## MS Exposure Settings

```{r exposure-settings}
knitr::kable(rd$exposure_summary, format = "latex", booktabs = TRUE, linesep = "",
             col.names = c("Band", "Shutter", "ISO", "F-Stop"),
             align = c("l", "c", "c", "c")) |>
  kableExtra::kable_styling(latex_options = c("hold_position", "striped"), full_width = FALSE)
```

## Quality Assessment

```{r quality-assessment}
# Basic radiometric checks. GPS is informational only — imagery is
# georeferenced downstream, so GPS jitter does not gate the verdict.
qa_df <- data.frame(
  Check = c("Lighting Consistency", "Exposure Consistency", "GPS (informational)", "Sun Sensor Stability"),
  Status = c(
    ifelse(rd$qa_results$lighting$pass, "PASS", "REVIEW"),
    ifelse(rd$qa_results$exposure$pass, "PASS", "FAIL"),
    "INFO",
    ifelse(rd$qa_results$sunsensor$pass, "PASS", "REVIEW")
  ),
  Detail = c(
    rd$qa_results$lighting$detail,
    rd$qa_results$exposure$detail,
    rd$qa_results$gps$detail,
    rd$qa_results$sunsensor$detail
  ),
  stringsAsFactors = FALSE
)

# Append advanced diagnostics if available
if (!is.null(rd$advanced_qa)) {
  adv <- rd$advanced_qa
  adv_df <- data.frame(
    Check = c("Altitude Stability", "Gimbal (Nadir)", "Capture Regularity",
              "Band Ratio Consistency", "Outlier Rate (MAD)", "Spatial Coverage"),
    Status = c(
      ifelse(adv$altitude$pass, "PASS", "FAIL"),
      ifelse(adv$gimbal$pass, "PASS", "FAIL"),
      ifelse(adv$capture_interval$pass, "PASS", "FAIL"),
      ifelse(adv$band_ratios$pass, "PASS", "REVIEW"),
      ifelse(adv$outliers$pass, "PASS", "FAIL"),
      ifelse(adv$coverage$pass, "PASS", "REVIEW")
    ),
    Detail = c(
      adv$altitude$detail,
      adv$gimbal$detail,
      adv$capture_interval$detail,
      adv$band_ratios$detail,
      adv$outliers$detail,
      adv$coverage$detail
    ),
    stringsAsFactors = FALSE
  )
  qa_df <- rbind(qa_df, adv_df)
}

knitr::kable(qa_df, format = "latex", booktabs = TRUE, linesep = "",
             col.names = c("Check", "Status", "Detail"),
             align = c("l", "c", "l")) |>
  kableExtra::kable_styling(latex_options = "hold_position", full_width = TRUE) |>
  kableExtra::column_spec(1, bold = TRUE)
```

## Band Stability Scores

```{r band-stability}
knitr::kable(rd$band_stability, format = "latex", booktabs = TRUE, linesep = "",
             col.names = c("Band", "Score", "Status"),
             align = c("l", "c", "c")) |>
  kableExtra::kable_styling(latex_options = c("hold_position", "striped"), full_width = FALSE)
```

```{r lighting-summary, results='asis'}
if (!is.null(rd$lighting_summary)) {
  cat("\n\n## Lighting Consistency by Band\n\n")
  cat("\\small Irradiance detrended by solar elevation; cloud events detected via rolling-median MAD z-score.\n\n")
  print(
    knitr::kable(rd$lighting_summary, format = "latex", booktabs = TRUE, linesep = "",
                 col.names = c("Band", "Classification", "Detrended CV", "Cloud Events", "Score"),
                 align = c("l", "l", "c", "c", "c")) |>
      kableExtra::kable_styling(latex_options = c("hold_position", "striped"), full_width = FALSE)
  )
}
```

```{r outlier-table, results='asis'}
if (!is.null(rd$advanced_qa) && !is.null(rd$advanced_qa$outliers$per_band)) {
  cat("\n\n## Outlier Detection (Modified Z-Score)\n\n")
  cat("\\small Method: MAD-based Modified Z-Score (Iglewicz \\& Hoaglin, 1993). Threshold: $|Z| > 3.5$\n\n")
  print(
    knitr::kable(rd$advanced_qa$outliers$per_band, format = "latex", booktabs = TRUE, linesep = "",
                 col.names = c("Band", "Total", "Outliers", "\\% Outliers"),
                 align = c("l", "r", "r", "r")) |>
      kableExtra::kable_styling(latex_options = c("hold_position", "striped"), full_width = FALSE)
  )
}
```

\vspace{8pt}

```{r overall-verdict, results='asis'}
if (rd$overall_pass) {
  cat("\\begin{center}")
  cat("\\colorbox{passgreen!15}{\\parbox{0.9\\textwidth}{")
  cat("\\centering\\large\\bfseries\\color{passgreen} OVERALL: PASS")
  cat("\\\\\\normalsize\\normalfont All quality checks within acceptable limits.")
  cat("}}")
  cat("\\end{center}")
} else {
  cat("\\begin{center}")
  cat("\\colorbox{revieworange!15}{\\parbox{0.9\\textwidth}{")
  cat("\\centering\\large\\bfseries\\color{revieworange} OVERALL: REVIEW NEEDED")
  if (length(rd$issues) > 0) {
    cat("\\\\\\normalsize\\normalfont ", paste(rd$issues, collapse = "; "))
  }
  cat("}}")
  cat("\\end{center}")
}
```

```{r operator-notes, results='asis'}
if (nchar(trimws(rd$notes)) > 0) {
  cat("\n\n## Operator Notes\n\n")
  cat(rd$notes)
}
```
